The large scale clustering of fast radio bursts in dispersion measure space

### 2015-04-01 writeup/dm_space_distortions.tex
Cleaned up limber.

@@

Alternately, on the flat sky and for small angles:
\begin{align}
(2\pi)^2\delta^2(\vec \ell - \vec \ell')C_\ell(\chi, \chi')
    &=
        \int\ud^2\vec\theta\ud^2\vec\theta'
        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
        \\
    &= gg'aa'
        \int\ud^2\vec\theta\ud^2\vec\theta'
        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)
        \\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i k_\parallel (\chi - \chi')} P(k, 0)
        \int\ud^2\vec\theta e^{-i(\vec\ell-\bar\chi\vec k_\bot)\cdot\vec\theta}
        \int\ud^2\vec\theta' e^{-i(\vec\ell'-\bar\chi\vec k_\bot)\cdot\vec\theta'}
        \\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, 0)
        (2\pi)^4 \delta^2(\vec\ell - \bar\chi \vec k_\bot)
        \delta^2(\vec\ell' - \bar\chi\vec k_\bot)
        \\
    &= gg'aa'
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
        \frac{(2\pi)^2\delta^2(\vec\ell' - \vec \ell)}{\bar\chi^2}
        \\
C_\ell(\chi, \chi')
    &= \frac{gg'aa'}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
\end{align}
Which is valid for $\ell \gg 1$ and $\chi - \chi' \ll \bar\chi$.
$\bar \chi \equiv (\chi + \chi') /2$

Or for flat sky and small angles:
\begin{align}
C^{dd}_\ell(\chi,\chi') 
    &=
    \int_0^\chi\ud\chi''g''a''
    \int_0^{\chi'}\ud\chi'''g'''a'''
    \frac{1}{\bar\chi^2}
    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
    e^{i k_\parallel (\chi'' - \chi''')}
    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, 0)
    \\
    &\approx
    \int_0^\chi\ud\chi''g''a''
    \int_0^{\chi'}\ud\chi'''g'''a'''
    \frac{1}{\bar\chi^2}
    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
    e^{i k_\parallel (\chi'' - \chi''')}
    P_{ee}(\ell/\bar\chi, 0)
    \\
    &=
    \int_0^\chi\ud\chi''g''a''
    \int_0^{\chi'}\ud\chi'''g'''a'''
    \frac{1}{\bar\chi^2}
    \delta(\chi'' - \chi''')
    P_{ee}(\ell/\bar\chi, 0)
    \\
    &=
    \int_0^{\min(\chi,\chi')}\ud\chi''
    \left(\frac{g''a''}{\chi''}\right)^2
    P_{ee}(\ell/\chi'', 0)
\end{align}
\red{Double check the $\min$.}
where the second line applies Limber's approximation.

Or under Limber:
\begin{align}
C^{dx}_\ell(\chi,\chi')
    &=
    g'a'
    \int_0^\chi\ud\chi''g''a''
    \frac{1}{\bar\chi^2}
    \delta(\chi'' - \chi')
    P_{ex}(\ell/\bar\chi, 0)
    \\
    &=
    \left(\frac{g'a'}{\chi'}\right)^2
    P_{ex}(\ell/\chi', 0)
    \qquad \textrm{if $\chi' < \chi$ and 0 otherwise.}
    \\
C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
    &=
    \left(\frac{g^ma^m}{\chi^m}\right)^2
    P_{ex}(\ell/\chi^m, 0)
\end{align}

Accumulating all terms for Limber and assuming a linear bias model:
\begin{align}
C^{ss}_\ell(\chi_m,\Delta\chi) =&~
    (b_f - b_e)^2 \left(\frac{g_m a_m}{\chi_m}\right)^2
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel \Delta\chi}
        P(\sqrt{k_\parallel^2 + \ell^2/\chi_m^2}, 0)
    \\ &+
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    + \frac{2}{\chi} \right)_{\chi_m}^2
    b_e^2 \int_0^{\chi_m}\ud\chi''
        \left(\frac{g''a''}{\chi''}\right)^2
        P(\ell/\chi'', 0)
    \\ &+
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    + \frac{2}{\chi} \right)_{\chi_m}
    b_e(b_f - b_e)\left(\frac{g_m a_m}{\chi_m}\right)^2
        P(\ell/\chi_m, 0)
\end{align}

%%%% SCRAP

\begin{comment}
\begin{align}
w(\hat n \cdot \hat n', \chi, \chi') 
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
        e^{i\vec k \cdot \vec x} e^{i\vec k' \cdot \vec x'}
        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k, 0)\\
    &= gg'aa'
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k)\\
    &= gg'aa'
        \int\frac{k^2 \sin(\theta_k) \ud k \ud \theta_k \ud \phi_k}{(2 \pi)^3} 
        e^{i k |\vec x - \vec x'| \cos\theta_k} P(k, 0)\\
    &= gg'aa'
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        \frac{\sin(k |\vec x - \vec x'|)}{k |\vec x - \vec x'|} P(k, 0)\\
    &= gg'aa'
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        j_0 (k \sqrt{\chi^2 + \chi'^{^2} - \chi \chi' \hat n \cdot \hat n'})
        P(k, 0)
\end{align}
Somehow when I integrate this against a Legendre polynomial, $P_\ell(\mu)$,
to get $C_\ell$
I'm going to get Bessel functions. Lets assume that works (Kris, how does this
work?) to get:
\begin{equation}
    C_{\ell\chi\chi'} = \frac{2 gg'aa'}{\pi}
    \int_0^\infty\ud k k^2 j_\ell(k \chi) j_\ell(k \chi')
        P(k, 0)
\end{equation}
\end{comment}

\begin{comment}
\begin{align}
    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
    &= \int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
         \langle \delta_e(\hat n \chi'') \delta_e(\hat n' \chi''') \rangle\\
    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
        g''g'''a''a'''
        \int\frac{\ud^3\vec k}{(2 \pi)^3} \frac{\ud^3\vec k'}{(2 \pi)^3}
        e^{i\vec k \cdot \vec x''} e^{i\vec k' \cdot \vec x'''}
        \langle \delta(\vec k, 0) \delta(\vec k', 0) \rangle\\
    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
        g''g'''a''a'''
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        j_0 (k \sqrt{\chi''^2 + \chi'''^{^2} - \chi'' \chi''' \hat n \cdot \hat n'})
        P(k, 0)
\end{align}

Alternately, we can make the limber approximation (replacing
$a(\chi'')g(\chi'')$ and $a(\chi''')g(\chi''')$ with 
$a(\bar \chi)g(\bar \chi)$) and small angle approximations
(replacing the argument of the spherical Bessel with
$k\sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2}$).
\begin{align}
    w^{dd}(\hat n \cdot \hat n', \chi, \chi')
    &= b_e^2\int_0^\chi \ud \chi'' \int_0^{\chi'} \ud \chi'''
        (g(\bar \chi) a(\bar \chi))^2
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})
        P(k, 0)\\
    &= b_e^2\int_0^{(\chi + \chi')/2} \ud \bar\chi 
        (g(\bar \chi) a(\bar \chi))^2
        \int_0^\infty\frac{\ud k}{2 \pi^2} k^2
        P(k, 0)
        \int_{-\infty}^{\infty} \ud \Delta\chi
        j_0 (k \sqrt{\Delta \chi^2 + (\bar \chi (\hat n - \hat n'))^2})\\
\end{align}

\end{comment}

>>>>

Assembling terms:
\begin{align}
C^{ss}_\ell(\chi,\chi') = &
    \frac{2}{\pi}
    \int_0^\infty\ud k k^2
    j_\ell(k\chi) j_{\ell}(k\chi')
    \left[ P_{ff}(k, \bar\chi)
    + P_{ee}(k, \bar\chi)
    - 2P_{fe}(k, \bar\chi) \right]
    \nonumber\\
    & +
    \frac{2}{\pi}
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    + \frac{2}{\chi} \right)
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
    + \frac{2}{\chi'} \right)
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
    P_{ee}(k, (\chi''+\chi''')/2)
    \nonumber\\
    & +
    \frac{2}{\pi}
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}
    + \frac{2}{\chi} \right)
    \int_0^\chi\ud\chi''
    \int_0^\infty\ud k k^2 
    j_\ell(k\chi') j_{\ell}(k\chi'')
    \left[ P_{ee}(k, (\chi' + \chi'')/2)
    - P_{fe}(k, (\chi' + \chi'')/2) \right]
    \nonumber\\
    & +
    \frac{2}{\pi}
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi'}
    + \frac{2}{\chi'} \right)
    \int_0^{\chi'}\ud\chi''
    \int_0^\infty\ud k k^2 
    j_\ell(k\chi) j_{\ell}(k\chi'')
    \left[ P_{ee}(k, (\chi + \chi'')/2)
    - P_{fe}(k, (\chi + \chi'')/2) \right]
\end{align}

@@

Alternately, on the flat sky and for small angles:
\begin{align}
(2\pi)^2\delta^2(\vec \ell - \vec \ell')C_\ell(\chi, \chi')
    &=
        \int\ud^2\vec\theta\ud^2\vec\theta'
        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
        \langle \delta(\hat n \chi) \delta(\hat n' \chi') \rangle
        \\
    &\approx
        \int\ud^2\vec\theta\ud^2\vec\theta'
        e^{-i\vec\ell\cdot\vec\theta} e^{-i\vec\ell'\cdot\vec\theta'}
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i\vec k \cdot (\vec x - \vec x')} P(k, \bar\chi)
        \\
    &=
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i k_\parallel (\chi - \chi')} P(k, \bar\chi)
        \int\ud^2\vec\theta e^{-i(\vec\ell-\bar\chi\vec k_\bot)\cdot\vec\theta}
        \int\ud^2\vec\theta' e^{-i(\vec\ell'-\bar\chi\vec k_\bot)\cdot\vec\theta'}
        \\
    &=
        \int\frac{\ud^3\vec k}{(2 \pi)^3} 
        e^{i k_\parallel (\chi - \chi')} P(\sqrt{k_\parallel^2 + k_\bot^2}, \bar\chi)
        (2\pi)^4 \delta^2(\vec\ell - \bar\chi \vec k_\bot)
        \delta^2(\vec\ell' - \bar\chi\vec k_\bot)
        \\
    &=
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
        \frac{(2\pi)^2\delta^2(\vec\ell' - \vec \ell)}{\bar\chi^2}
        \\
C_\ell(\chi, \chi')
    &= \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
\end{align}
Which is valid for $\ell \gg 1$ and $\chi - \chi' \ll \bar\chi$.
$\bar \chi \equiv (\chi + \chi') /2$

Or for flat sky and small angles:
\begin{align}
C^{dd}_\ell(\chi,\chi') 
    &=
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \frac{1}{\bar\chi^{\prime 2}}
    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
    e^{i k_\parallel (\chi'' - \chi''')}
    P_{ee}(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, (\chi'' + \chi''')/2)
    \\
    &\approx
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \frac{1}{\bar\chi^{\prime 2}}
    \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
    e^{i k_\parallel (\chi'' - \chi''')}
    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
    \\
    &=
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \frac{1}{\bar\chi^{\prime 2}}
    \delta(\chi'' - \chi''')
    P_{ee}(\ell/\bar\chi', (\chi'' + \chi''')/2)
    \\
    &=
    \int_0^{\min(\chi,\chi')}\ud\chi''
    \left(\frac{1}{\chi''}\right)^2
    P_{ee}(\ell/\chi'', \chi'')
\end{align}
where the second line applies Limber's approximation. 
$\bar\chi' \equiv (\chi'' + \chi''')/2$.

Or under Limber:
\begin{align}
C^{dx}_\ell(\chi,\chi')
    &=
    \int_0^\chi\ud\chi''
    \frac{1}{\bar\chi^{\prime 2}}
    \delta(\chi'' - \chi')
    P_{ex}(\ell/{\bar\chi'}, (\chi'' + \chi')/2)
    \\
    &=
    \left(\frac{1}{\chi'}\right)^2
    P_{ex}(\ell/\chi', \chi')
    \qquad \textrm{if $\chi' < \chi$ and 0 otherwise.}
%    \\
%C^{dx}_\ell(\chi,\chi') + C^{xd}_\ell(\chi,\chi')
%    &=
%    \left(\frac{1}{\chi^m}\right)^2
%    P_{ex}(\ell/\chi^m, \chi_m)
\end{align}

Accumulating all terms for Limber and assuming a linear bias model:
\begin{align}
C^{ss}_\ell(\chi, \chi') =&~
    \left(\frac{b_f - b_e }{\bar\chi}\right)^2
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel \Delta\chi}
        P(\sqrt{k_\parallel^2 + \ell^2/\bar\chi^2}, \bar\chi)
    \\ &+
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
    + \frac{2}{\chi_m} \right)^2
    b_e^2 \int_0^{\chi_m}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
        P(\ell/\chi'',\chi'')
    \\ &+
    \left(\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi_m}
    + \frac{2}{\chi_m} \right)
    \frac{b_e(b_f - b_e)}{\chi_m^2}
        P(\ell/\chi_m, \chi_m)
\end{align}
where $\chi_m \equiv \min(\chi, \chi')$.
